\documentclass[]{article}
\voffset=-1.5cm
\oddsidemargin=0.0cm
\textwidth = 480pt


\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{framed}
\usepackage{multicol}
%\usepackage[paperwidth=21cm, paperheight=29.8cm]{geometry}
%\usepackage[angle=0,scale=1,color=black,hshift=-0.4cm,vshift=15cm]{background}
%\usepackage{multirow}
\usepackage{enumerate}

\usepackage{amsmath,amsfonts,amssymb}
\usepackage{color}
\usepackage{multirow}
\usepackage{eurosym}
\usepackage{framed}
\usepackage{enumerate}
%\graphicspath{ {images/} }
%\input def.tex
%\input dsdef.tex
%\input rgb.tex

%\newcommand \la{\lambda}
%\newcommand \al{a}
%\newcommand \be{b}
\newcommand \x{\overline{x}}
\newcommand \y{\overline{y}}
\begin{document}

\begin{enumerate}
\item (a) Define what is meant by a minimax strategy in a 2-player game. 3 %
(b) For the following matrix game
A B
A (5,3) (4,4)
B (2,6) (4,4)
Find the minimax strategies and payoffs for each player. If both players
play their minimax strategies, what is the value of the game ? 10 %
(c) In the context of a 2-person game, define what a Nash equilibrium is. 3 %
%---------------------------------------------------%
\item (a) In the context of a 2-person game, define what a Nash equilibrium is. 3
(b) What is a pure strategy ? What is a mixed strategy ? 3
(c) For strategies define strict dominance and weak dominance. 3
(d) By removing all strategies which are dominated by strict pure or mixed
strategies, derive the reduced version of the following 2-player matrix
game:
D E F
A (3,5) (5,1) (1,2)
B (1,1) (6,9) (6,4)
C (2,6) (4,7) (0,8)
8
(e) Derive the Nash equilibria and values of this game. 8
%----------------------------------------------------%
\item 

\begin{enumerate}[(a)]
\item In the context of a 2-person game, define what a Nash equilibrium is. 3
\item What is a pure strategy ? What is a mixed strategy ? 3
\item For strategies define strict dominance and weak dominance. 3
\item By removing all strategies which are dominated by strict pure or mixed
strategies, derive the reduced version of the following 2-player matrix
game:
D E F
A (4,-2) (3,0) (-3,-1)
B (-1,1) (2,2) (2,3)
C (2,1) (-1,-1) (0,4)
8
\item  Derive the Nash equilibria and values of this game. 8
\end{enumerate}
%-------------------------------------------------%

\item Mark Burk 2015 Q2
\begin{enumerate}[(a)]
\item  In terms of a strategic (matrix) game, what is a dominated strategy?
Describe the technique of iterated elimination of dominated strategies.
What is the technique used for ? 5
\item By removing all strategies which are dominated by strict pure or mixed
strategies, derive the reduced version of the following 2-player zerosum
matrix game:
D E F
A (5,-5) (1,-1) (2,-2)
B (1,-1) (0,0) (3,-3)
C (2,-2) (3,-3) (6,-6)
8
\item In terms of a 2-player zero-sum game, what is a minimax strategy? 3
\item Derive the minimax strategies and value of the above game. 9
\end{enumerate}
%--------------------------------------------------%



\item An industry contains two firms, one whose cost function is TC(y) = 30y and another whose cost function is TC(y) = $y^2$. The inverse demand function for the firms' output is $p = 120 - Q$, where $Q$ is the total output. What are the firms' outputs in a Nash equilibrium of Cournot's model?

%- https://www.economics.utoronto.ca/osborne/2x3/tutorial/COURNX.HTM

%--------------------------------------------------%

\item- Cournot Duopoly
 %   - https://www.youtube.com/watch?v=An_2r6Ae_28

\item Cournot Duopoly
% https://www.youtube.com/watch?v=CmSlJ5XmwEU

\item Cournot Duopoly
% http://faculty.econ.ucdavis.edu/faculty/bonanno/teaching/200C/Cournot.pdf


\item 
% https://eml.berkeley.edu/~webfac/dellavigna/e101a_f06/fexam3solutions.pdf
% Page 5
%-------------------------------------------------%

% \item - https://www.youtube.com/watch?v=v5nznvFHzlE

\item - Cournot Duopoly
 %    https://www.youtube.com/watch?v=rQTf3oy0QUU


\item - Bertrand Duopoly (Identical Goods)
  %   https://www.youtube.com/watch?v=AKGllp9heEs

\item - Bertrand Duopoly (Differentiated Goods)
https://www.youtube.com/watch?v=YrnqUPW96lY

\item - Bertrand Duopoly
     https://www.youtube.com/watch?v=alE7u-9FRsQ

\item 
The costs incurred by a firm in a production period are
$c = 100 + 2x$
where x is the number of items produced in that period. The items sell
at a price of
$p = 10 − x/50$
each. Find the level of production that maximises the firm’s profits
when the firm has a monopoly. 
\item - Stackleberg
https://www.youtube.com/watch?v=LMCODkeeDtE

\item - Stackleberg
https://www.youtube.com/watch?v=57GmlmgKlZI
\end{enumerate}
\end{document}
%- Cournot
%- Sprting Clay
%- https://www.youtube.com/watch?v=An_2r6Ae_28

%==================%
%- Cournot
%- AH
%- https://www.youtube.com/watch?v=rQTf3oy0QUU

%==================%
% Bertrand Duopoly
% AH
% https://www.youtube.com/watch?v=alE7u-9FRsQ

%===================%

%- Oligopoly: Bertrand Competition with Identical Goods
%- https://www.youtube.com/watch?v=AKGllp9heEs
%- Sprting Clay

%===================%
%- Oligopoly: Bertrand Competition with Differentiated Goods
% https://www.youtube.com/watch?v=YrnqUPW96lY
%- Sprting Clay

%===================%
% Stackleberg
% Sporting Clay
% https://www.youtube.com/watch?v=LMCODkeeDtE

%===================%
% Stackleberg
% AH
% https://www.youtube.com/watch?v=57GmlmgKlZI

%===================%
%- Standby
%- https://www.economics.utoronto.ca/osborne/2x3/tutorial/COURNX.HTM
%- http://www.dummies.com/education/economics/how-to-compete-the-cournot-model-of-duopolies-in-managerial-economics/
%- http://www.sumonbhaumik.net/bs2243-lecture4.pdf
%- https://www0.gsb.columbia.edu/faculty/nsicherman/B7006-002/duopoly.pdf
%- https://www2.warwick.ac.uk/fac/soc/economics/staff/dsgroi/ec202/w03_monopoly_and_duopoly.pdf